NewAnalysis

### 2024-08-09 Code/NewAnalysis.Rmd
Did some work and using this file for testing what data to use

```{r}
anova(dash_and_hurdles_two_effect_gamma_log, dash_and_hurdles_three_effect_gamma_log)
```
What we observe is that there is not a significant difference between these
models as the p value is quite large.

Lets compare the two models
```{r}
summary(dash_and_hurdles_three_effect_gamma_log)
summary(hurdles_two_effect_gamma_log)
```
Now we will see how the inclusion of the pooled data will influence the results
```{r}
sim_three_effect_time <- function(model, base, RxnTime) {
  simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    sd_Venue <- vc$sdcor[1]
    sd_Venue_heat <- vc$sdcor[2]
    sd_event <- vc$sdcor[3]

@@

Now we test
```{r}
set.seed(1)
sim_three_effect_time(dash_and_hurdles_three_effect_gamma_log, dash_and_hurdles_one_gamma_log, 0.1)
```
## Now for women
We want to make sure we get similar results when we pool the women's 100m hurdle
and 100m dash. 
```{r}
times <- read.csv("../Data/GLMMData.csv")
colnames(times) <- c("Venue", "Type", "Time", "RxnTime", "Gender", "Heat", "Event")
```

@@

```{r}
library(car)
TukeyHSD(aov(RxnTime ~ Event, data = all_events))
```
We see that the 200m dash differs significantly from 100m dash/hurdles

>>>>

```{r}
anova(dash_and_hurdles_two_effect_gamma_log, dash_and_hurdles_three_effect_gamma_log)
```
What we observe is that there is not a significant difference between these
models as the p value is quite large. Thus we will not include `Event` as a
feature in our final model.

Now we will see how the inclusion of the pooled data will influence the results
```{r}
sim_three_effect_time <- function(model, base, RxnTime) {
  simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    sd_Venue <- vc$sdcor[1]
    sd_Venue_heat <- vc$sdcor[2]
    sd_event <- vc$sdcor[3]

@@

@@

```{r}
library(car)
TukeyHSD(aov(RxnTime ~ Event, data = all_events))
```
Using a Tukey's Honestly Significant Difference test, we see that the 200m dash
differs significantly from 100m dash/hurdles.

Based on all the following evidence we are going to perform our men's analysis
on data from the 100 meter dash and 110 meter hurdles exclusively.

## Now for women
We want to make sure we get similar results when we pool the women's 100m hurdle
and 100m dash. 
```{r}
times <- read.csv("../Data/GLMMData.csv")
colnames(times) <- c("Venue", "Type", "Time", "RxnTime", "Gender", "Heat", "Event")
```
